---
This Script will read the spot segmentation data from the screen for HBEC cells and generate the relative change in transcription site frequency 
---


```{r}
library(readr)
library (dplyr)
library(ggplot2)
library(plyr)
library(tidyverse)
library(knitr)
library(SpatialTools)
library(reshape2)
library(data.table)
library(tidyr)
library(RColorBrewer)
library(gplots)
```
                                Reading data

- Reading spot segmentation data for all genes
- Data for rab7a and slc2a1 , rpap3 and sec16a was imaged form the same plate but in two experiment files as the plate orientation was flipped in the initial imaging

```{r}
pat<- "*Nuclei*"

paths_Slc2a1 <- dir (path = "Data/Slc2a1/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Slc2a1) <- basename(paths_Slc2a1)
total.data_Slc2a1 <-ldply (paths_Slc2a1, fread , sep = "\t")
intensity.data_Slc2a1 <- total.data_Slc2a1[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Slc2a1,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Canx <- dir (path = "Data/Canx/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Canx) <- basename(paths_Canx)
total.data_Canx <-ldply (paths_Canx, fread , sep = "\t")
intensity.data_Canx <- total.data_Canx[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Canx,"Nuclei Selected - Number of Spots" , "Spot" )


paths_Errfi1 <- dir (path = "Data/Errfi1/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Errfi1) <- basename(paths_Errfi1)
total.data_Errfi1 <-ldply (paths_Errfi1, fread , sep = "\t")
intensity.data_Errfi1 <- total.data_Errfi1[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Errfi1,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Rab7a <- dir (path = "Data/Rab7a/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Rab7a) <- basename(paths_Rab7a)
total.data_Rab7a <-ldply (paths_Rab7a, fread , sep = "\t")
intensity.data_Rab7a <- total.data_Rab7a[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Rab7a,"Nuclei Selected - Number of Spots" , "Spot" )



paths_Dnajc5 <- dir (path = "Data/Dnajc5/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Dnajc5) <- basename(paths_Dnajc5)
total.data_Dnajc5 <-ldply (paths_Dnajc5, fread , sep = "\t")
intensity.data_Dnajc5 <- total.data_Dnajc5[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Dnajc5,"Nuclei Selected - Number of Spots" , "Spot" )


paths_GAPDH <- dir (path = "Data/GAPDH/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_GAPDH) <- basename(paths_GAPDH)
total.data_GAPDH <-ldply (paths_GAPDH, fread , sep = "\t")
intensity.data_GAPDH <- total.data_GAPDH[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_GAPDH,"Nuclei Selected - Number of Spots" , "Spot" )



paths_RhoA <- dir (path = "Data/RhoA/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_RhoA) <- basename(paths_RhoA)
total.data_RhoA <-ldply (paths_RhoA, fread , sep = "\t")
intensity.data_RhoA <- total.data_RhoA[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_RhoA,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Rpap3 <- dir (path = "Data/Rpap3/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Rpap3) <- basename(paths_Rpap3)
total.data_Rpap3 <-ldply (paths_Rpap3, fread , sep = "\t")
intensity.data_Rpap3 <- total.data_Rpap3[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Rpap3,"Nuclei Selected - Number of Spots" , "Spot" )



paths_Myc <- dir (path = "Data/Myc/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Myc) <- basename(paths_Myc)
total.data_Myc <-ldply (paths_Myc, fread , sep = "\t")
intensity.data_Myc <- total.data_Myc[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Myc,"Nuclei Selected - Number of Spots" , "Spot" )


paths_Sec16a <- dir (path = "Data/Sec16a/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Sec16a) <- basename(paths_Sec16a)
total.data_Sec16a <-ldply (paths_Sec16a, fread , sep = "\t")
intensity.data_Sec16a <- total.data_Sec16a[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Sec16a,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Kpnb1 <- dir (path = "Data/Kpnb1/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Kpnb1) <- basename(paths_Kpnb1)
total.data_Kpnb1 <-ldply (paths_Kpnb1, fread , sep = "\t")
intensity.data_Kpnb1 <- total.data_Kpnb1[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Kpnb1,"Nuclei Selected - Number of Spots" , "Spot" )

paths_egfr <- dir (path = "Data/egfr/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_egfr) <- basename(paths_egfr)
total.data_egfr <-ldply (paths_egfr, fread , sep = "\t")
intensity.data_egfr <- total.data_egfr[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_egfr,"Nuclei Selected - Number of Spots" , "Spot" )

paths_nras <- dir (path = "Data/nras/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_nras) <- basename(paths_nras)
total.data_nras <-ldply (paths_nras, fread , sep = "\t")
intensity.data_nras <- total.data_nras[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_nras,"Nuclei Selected - Number of Spots" , "Spot" )


paths_P53 <- dir (path = "Data/P53/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_P53) <- basename(paths_P53)
total.data_P53 <-ldply (paths_P53, fread , sep = "\t")
intensity.data_P53 <- total.data_P53[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_P53,"Nuclei Selected - Number of Spots" , "Spot" )


################## left overs######### as they were flipped


paths_Sec16a_left_over <- dir (path = "Data/Sec16a_left_over/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Sec16a_left_over) <- basename(paths_Sec16a_left_over)
total.data_Sec16a_left_over <-ldply (paths_Sec16a_left_over, fread , sep = "\t")
intensity.data_Sec16a_left_over <- total.data_Sec16a_left_over[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Sec16a_left_over,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Rpap3_left_over <- dir (path = "Data/Rpap3_left_over/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Rpap3_left_over) <- basename(paths_Rpap3_left_over)
total.data_Rpap3_left_over <-ldply (paths_Rpap3_left_over, fread , sep = "\t")
intensity.data_Rpap3_left_over <- total.data_Rpap3_left_over[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Rpap3_left_over,"Nuclei Selected - Number of Spots" , "Spot" )



paths_Slc2a1_left_over <- dir (path = "Data/Slc2a1_left_over/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Slc2a1_left_over) <- basename(paths_Slc2a1_left_over)
total.data_Slc2a1_left_over <-ldply (paths_Slc2a1_left_over, fread , sep = "\t")
intensity.data_Slc2a1_left_over <- total.data_Slc2a1_left_over[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Slc2a1_left_over,"Nuclei Selected - Number of Spots" , "Spot" )



paths_Rab7a_left_over <- dir (path = "Data/Rab7a_left_over/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Rab7a_left_over) <- basename(paths_Rab7a_left_over)
total.data_Rab7a_left_over <-ldply (paths_Rab7a_left_over, fread , sep = "\t")
intensity.data_Rab7a_left_over <- total.data_Rab7a_left_over[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Rab7a_left_over,"Nuclei Selected - Number of Spots" , "Spot" )
 
```

- Calculating  mean of the spot number

```{r}
Freq_Errfi1 <- intensity.data_Errfi1 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Errfi1 = mean (Spot)) 


Freq_Canx <- intensity.data_Canx %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Canx = mean (Spot)) 



Freq_egfr <- intensity.data_egfr %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Egfr = mean (Spot)) 

Freq_GAPDH <- intensity.data_GAPDH %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Gapdh = mean (Spot)) 


Freq_Kpnb1 <- intensity.data_Kpnb1 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Kpnb1 = mean (Spot)) 


Freq_Myc <- intensity.data_Myc %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Myc = mean (Spot)) 


Freq_P53 <- intensity.data_P53 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_P53 = mean (Spot)) 


Freq_RhoA <- intensity.data_RhoA %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_RhoA = mean (Spot)) 



Freq_Sec16a <- intensity.data_Sec16a %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Sec16a = mean (Spot)) 


Freq_Slc2a1 <- intensity.data_Slc2a1 %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Slc2a1 = mean (Spot)) 


 Freq_nras <- intensity.data_nras %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Nras = mean (Spot)) 
 
 Freq_Dnajc5 <- intensity.data_Dnajc5 %>% 
  as_tibble%>% 
 group_by(WellName)%>%dplyr:::summarize ( Mean_Dnajc5 = mean (Spot)) 

 Freq_Rab7a <- intensity.data_Rab7a %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rab7a = mean (Spot)) 

 Freq_Rpap3 <- intensity.data_Rpap3 %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rpap3 = mean (Spot)) 
 
 
Freq_Slc2a1 <- intensity.data_Slc2a1 %>% 
  as_tibble%>% 
 group_by(WellName)%>%dplyr:::summarize ( Mean_Slc2a1 = mean (Spot)) 

################## left overs######### 


Freq_Slc2a1_left_over <- intensity.data_Slc2a1_left_over %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Slc2a1_L = mean (Spot)) 



Freq_Rab7a_left_over <- intensity.data_Rab7a_left_over %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rab7a_L = mean (Spot)) 


Freq_Rpap3_left_over <- intensity.data_Rpap3_left_over %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rpap3_L = mean (Spot)) 


Freq_Sec16a_left_over <- intensity.data_Sec16a_left_over %>% 
  as_tibble%>% 
 group_by(WellName)%>%dplyr:::summarize ( Mean_Sec16a_L = mean (Spot)) 





# combing the flipped and non flipped data. This is mostly for the non flipped data processing later 1. Combining the data. 2. Renaming the Freq Columns and selecting the Freq Columns

 
 Freq_Combined_by_wellname <- Freq_Canx%>%
  full_join(Freq_egfr, by = "WellName")%>%
  full_join(Freq_Errfi1, by = "WellName")%>%
  full_join(Freq_GAPDH, by = "WellName")%>%
  full_join(Freq_Kpnb1, by = "WellName")%>%
  full_join(Freq_Myc, by = "WellName")%>%
  full_join(Freq_P53, by = "WellName")%>%
  full_join(Freq_Rab7a, by = "WellName")%>%
   full_join(Freq_Rab7a_left_over, by = "WellName")%>%
   full_join(Freq_Sec16a_left_over, by = "WellName")%>%
   full_join(Freq_Rpap3_left_over, by = "WellName")%>%
  full_join(Freq_RhoA, by = "WellName")%>%
  full_join(Freq_Sec16a, by = "WellName")%>%
  full_join(Freq_nras, by = "WellName")%>%
   full_join(Freq_Dnajc5, by = "WellName")%>%
   full_join(Freq_Rpap3, by = "WellName")%>%
  full_join(Freq_Slc2a1, by = "WellName")%>%
 full_join(Freq_Slc2a1_left_over, by = "WellName")
 
Freq_Combined_by_wellname<-Freq_Combined_by_wellname
colnames(Freq_Combined_by_wellname)
```

- removing the "Mean" prefix and sorting out the non flipped ones in "Non_flipped_Mean12"


```{r}
Two_column_Mean_combined<- Freq_Combined_by_wellname%>%select(WellName, contains("Mean")) %>% dplyr:::rename (Canx= Mean_Canx,
                                                                      Errfi1=Mean_Errfi1,
                                                                      Egfr=Mean_Egfr,
                                                                      Gapdh=Mean_Gapdh,
                                                                      Kpnb1=Mean_Kpnb1,
                                                                      Myc=Mean_Myc,
                                                                      P53=Mean_P53,
                                                                      Rab7a=Mean_Rab7a,
                                                                      Rpap3_L=Mean_Rpap3_L,
                                                                      Sec16a_L=Mean_Sec16a_L,
                                                                      Rab7a_L=Mean_Rab7a_L,
                                                                      Slc2a1_L=Mean_Slc2a1_L,
                                                                      RhoA=Mean_RhoA,
                                                                      Sec16a=Mean_Sec16a,
                                                                      NRAS = Mean_Nras,
                                                                      Dnajc5=Mean_Dnajc5,
                                                                      Slc2a1=Mean_Slc2a1,
                                                                      Rpap3=Mean_Rpap3)


colnames(Two_column_Mean_combined)

Non_flipped_Mean12<-Two_column_Mean_combined[c(1,2,3,4,5,6,7,8,13,15,16)]

colnames(Non_flipped_Mean12)
```


Correcting the well names for the genes Rab7a, Slc2a1, Rpap3 and Sec16a
a. Use the mean frequency file of above genes to join with  "wellnames", which were actually flipped
b. Rename the fliped well names to correct "Wellnames" (the actual correct orientation wellnames) and join rest of imaging  the "left over" 
c. Combine data for all the genes


```{r}




template<- read.csv(file = "Metadata/Orginal_Flipped.csv")

Mean_Combined_by_wellname_flipped <- template%>%full_join(Freq_Rab7a, by = "WellName")%>%
full_join(Freq_Slc2a1, by = "WellName")%>%
full_join(Freq_Sec16a, by = "WellName")%>%
full_join(Freq_Rpap3, by = "WellName")




colnames(Mean_Combined_by_wellname_flipped)[c(1:2)]<-c("Original", "WellName")
 

 Mean_Combined_by_wellname_flipped_all<- Mean_Combined_by_wellname_flipped %>%
   full_join(Freq_Rab7a_left_over, by = "WellName")%>%
   full_join(Freq_Sec16a_left_over, by = "WellName")%>%
   full_join(Freq_Rpap3_left_over, by = "WellName")%>%
   full_join(Freq_Slc2a1_left_over, by = "WellName")%>%select(c(1:2),contains("Mean") )
 
colnames(Mean_Combined_by_wellname_flipped_all)
 
 
Mean_Combined_by_wellname_flipped_all<- Mean_Combined_by_wellname_flipped_all%>%
  mutate(Rab7s_final= rowMeans((.[,c(3,7)]) ,na.rm=TRUE))%>%
   mutate(Slc2a1_final= rowMeans((.[,c(4,10)]) ,na.rm=TRUE))%>%
   mutate(Sec16a_final= rowMeans((.[,c(5,8)]) ,na.rm=TRUE))%>%
   mutate(Rpap3_final= rowMeans((.[,c(6,9)]) ,na.rm=TRUE))%>%
  select(c(1:2),contains("Final") )
colnames(Mean_Combined_by_wellname_flipped_all)[c(3:6)]<-c ("Rab7a", "Slc2a1", "Sec16a", "Rpap3")
Mean_Combined_by_wellname_flipped_all<-Mean_Combined_by_wellname_flipped_all[c(-1)]

# joining flipped and non flipped


Full_Mean<- Non_flipped_Mean12%>% full_join(Mean_Combined_by_wellname_flipped_all, by = "WellName")
Full_Mean<-Full_Mean%>%select(c("WellName" ,"Canx", "Dnajc5" , "Egfr" , "Errfi1",  "Gapdh" , "Kpnb1", "Myc" ,  "NRAS" ,"P53"  ,    "Rab7a" , "Rpap3"  , "RhoA"   ,  "Sec16a"   ,      "Slc2a1"   ))
colnames(Full_Mean)
colnames(Full_Mean)[c(9)]<-"Nras"

write.csv(Full_Mean, "Output/Collated_Freq_HBEC_raw_unfiltered.csv", row.names = FALSE)

```


- Getting Stats


```{r}
#Convering into 2 colums dataframe to get the stats, in order to remove the outliars use 5x the range from the lower and upper quartile to get the min and max
#Full_Mean_pivot<-Full_Mean[c(-1)]

Full_Mean_b<- read.csv(file = "Output/Collated_Freq_HBEC_raw_unfiltered.csv")
sum(is.na(Full_Mean_b))



colnames(Full_Mean)


Full_Mean_pivot_b<-pivot_longer(Full_Mean_b, c(2:15), names_to = "Genes", values_to = "Mean")%>%na.omit
ggplot(Full_Mean_pivot_b, aes(y=Mean, color=Genes)) + geom_boxplot()


HBEC_Freq_Stat_bf<-Full_Mean_pivot_b%>%group_by(Genes)%>%dplyr:::summarize(
                                                         median = median(Mean),
                                                         high = quantile(Mean, 0.75)+ 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),
                                                         nintynine= quantile(Mean, 0.95),
                                                         five= quantile(Mean, 0.05),
                                                         max= max(Mean), min = min(Mean),
                                                         low = quantile(Mean, 0.25)- 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),
                                                          mean= mean(Mean) )
```

                      Generating the files for export
- Full join the Full_mean with rep1 , rep2 and untreated wells names "replicates_average_M"
- Putting the replicates side by side and calculating the mean of the treated
- Calculating the mean median mode of the untreated and exporting the file


```{r}
#### Reading the Replicates and Untreated well names for mean frequency 

Replicate1<- read.csv(file = 'Metadata/Replicate1.csv')
Replicate2<- read.csv(file = 'Metadata/Replicate2.csv')
Untreated<- read.csv(file = 'Metadata/Untreated.csv')

##### Exporting the replicate and untreated data

Replicate1_Data<-Replicate1%>%left_join(Full_Mean_b, by = "WellName")
Replicate2_Data<-Replicate2%>%left_join(Full_Mean_b, by = "WellName")
Untreated_Data<-Untreated%>%left_join(Full_Mean_b, by = "WellName")


 write.csv(Untreated_Data, "Output/HBEC_Freq_Untreated.csv", row.names=FALSE)







### printing the mean side by side#####

Side_By_side_HBEC<-cbind(Replicate1_Data[c(1,2)], Replicate2_Data[c(2,1)], 
            Replicate1_Data[c(1,3)], Replicate2_Data[c(3,1)],
            Replicate1_Data[c(1,4)], Replicate2_Data[c(4,1)],
            Replicate1_Data[c(1,5)], Replicate2_Data[c(5,1)],
            Replicate1_Data[c(1,6)], Replicate2_Data[c(6,1)],
            Replicate1_Data[c(1,7)], Replicate2_Data[c(7,1)],
            Replicate1_Data[c(1,8)], Replicate2_Data[c(8,1)],
            Replicate1_Data[c(1,9)], Replicate2_Data[c(9,1)],
            Replicate1_Data[c(1,10)], Replicate2_Data[c(10,1)],
            Replicate1_Data[c(1,11)], Replicate2_Data[c(11,1)],
            Replicate1_Data[c(1,12)], Replicate2_Data[c(12,1)],
            Replicate1_Data[c(1,13)], Replicate2_Data[c(13,1)],
            Replicate1_Data[c(1,14)], Replicate2_Data[c(14,1)],
            Replicate1_Data[c(1,15)], Replicate2_Data[c(15,1)]
            )
colnames(Side_By_side_HBEC)

# getting the values of the Mean
replicates_M<-Side_By_side_HBEC[c(1,4,2,3,6,7,10,11,14,15,18,19,22,23,26,27,30,31,34,35,38,39, 42,43,46,47,50,51,54,55)]
colnames(replicates_M)

#Taking the mean of replicates


replicates_average_M<-replicates_M%>%
  mutate(Canx_F = rowMeans((.[,3:4]) ,na.rm=TRUE))%>%
  mutate(Dnajc5_F = rowMeans((.[,5:6]) ,na.rm=TRUE))%>%
  mutate(Egfr_F = rowMeans((.[,7:8]) ,na.rm=TRUE))%>%
  mutate(Errfi1_F = rowMeans((.[,9:10]) ,na.rm=TRUE))%>%
  mutate(Gapdh_F = rowMeans((.[,11:12]) ,na.rm=TRUE))%>%
  mutate(Kpnb1_F = rowMeans((.[,13:14]) ,na.rm=TRUE))%>%
  mutate(Myc_F = rowMeans((.[,15:16]) ,na.rm=TRUE))%>%
   mutate(Nras_F = rowMeans((.[,17:18]) ,na.rm=TRUE))%>%
  mutate(P53_F = rowMeans((.[,19:20]) ,na.rm=TRUE))%>%
  mutate(Rab7a_F = rowMeans((.[,21:22]) ,na.rm=TRUE))%>%
  mutate(Rpap3_F = rowMeans((.[,23:24]) ,na.rm=TRUE))%>%
  mutate(RhoA_F = rowMeans((.[,25:26]) ,na.rm=TRUE))%>%
  mutate(Sec16a_F = rowMeans((.[,27:28]) ,na.rm=TRUE))%>%
  mutate(Slc2a1_F = rowMeans((.[,29:30]) ,na.rm=TRUE))
  
#subsetting the _F entries only

replicates_average_M<-replicates_average_M%>%select(c(1,2) , contains("_F", ignore.case = TRUE, vars = NULL) )  # change it to include Well name

colnames(replicates_average_M)

# mean median and SD for the untreated data

Mean_Untreated_Freq<-colMeans(Untreated_Data[sapply(Untreated_Data, is.numeric)], na.rm = TRUE)
test<- Untreated_Data[sapply(Untreated_Data, is.numeric)]
Median_Untreated_Freq<-apply(test,2,median,na.rm = TRUE)
SD_Untreated_freq<-apply(test,2,sd,na.rm = TRUE)
Median_Untreated_Freq
Mean_Untreated_Freq
Untreated_Mean_Median_SD<- cbind(Mean_Untreated_Freq,Median_Untreated_Freq, SD_Untreated_freq )
write.csv(Untreated_Mean_Median_SD, "Output/HBEC_Freq_Untreated_Mean_Median_SD.csv")


```
                      Generating the files for export

- Normalizing the values with "Mean" of untreated for both replicates and average from the dataframe "Untreated_Mean_Median_SD"
- exporting the final file with compound name and treated average


```{r}


replicates_average_mean_normalized<-replicates_average_M%>%
  mutate(Canx_F= Canx_F/1.98 )%>%
  mutate(Dnajc5_F= Dnajc5_F/1.69 )%>%
  mutate(Egfr_F= Egfr_F/1.66 )%>%
  mutate(Errfi1_F= Errfi1_F/.266 )%>%
  mutate(Gapdh_F= Gapdh_F/1.27 )%>%
  mutate(Kpnb1_F= Kpnb1_F/1.06 )%>%
  mutate(Myc_F= Myc_F/.395 )%>%
  mutate(Nras_F= Nras_F/.503 )%>%
  mutate(P53_F= P53_F/.315 )%>%
  mutate(Rab7a_F= Rab7a_F/2.045 )%>%
  mutate(Rpap3_F= Rpap3_F/.310 )%>%
  mutate(RhoA_F= RhoA_F/1.92 )%>%
  mutate(Sec16a_F= Sec16a_F/.37 )%>%
mutate(Slc2a1_F= Slc2a1_F/.63)
  
replicates_1_mean_normalized<-Replicate1_Data%>%
  mutate(Canx= Canx/1.98 )%>%
  mutate(Dnajc5= Dnajc5/1.69 )%>%
  mutate(Egfr= Egfr/1.66 )%>%
  mutate(Errfi1= Errfi1/.266 )%>%
  mutate(Gapdh= Gapdh/1.27 )%>%
  mutate(Kpnb1= Kpnb1/1.06 )%>%
  mutate(Myc= Myc/.395 )%>%
  mutate(Nras= Nras/.503 )%>%
  mutate(P53= P53/.315 )%>%
  mutate(Rab7a= Rab7a/2.045 )%>%
  mutate(Rpap3= Rpap3/.310 )%>%
  mutate(RhoA= RhoA/1.92 )%>%
  mutate(Sec16a= Sec16a/.37 )%>%
mutate(Slc2a1= Slc2a1/.63)

replicates_2_mean_normalized<-Replicate2_Data%>%
  mutate(Canx= Canx/1.98 )%>%
  mutate(Dnajc5= Dnajc5/1.69 )%>%
  mutate(Egfr= Egfr/1.66 )%>%
  mutate(Errfi1= Errfi1/.266 )%>%
  mutate(Gapdh= Gapdh/1.27 )%>%
  mutate(Kpnb1= Kpnb1/1.06 )%>%
  mutate(Myc= Myc/.395 )%>%
  mutate(Nras= Nras/.503 )%>%
  mutate(P53= P53/.315 )%>%
  mutate(Rab7a= Rab7a/2.045 )%>%
  mutate(Rpap3= Rpap3/.310 )%>%
  mutate(RhoA= RhoA/1.92 )%>%
  mutate(Sec16a= Sec16a/.37 )%>%
mutate(Slc2a1= Slc2a1/.63)






# renaming the columns

  colname<-colnames(replicates_average_mean_normalized)
  colname[1:2]<-c("WellName_R1", "WellName_R2")
  colnames(replicates_average_mean_normalized)<-colname
  

  

# using the existing list from xls attaching the compund name to the Mean data next to the well data 

WellNameCompound<- read.csv(file = 'Metadata/WellNameCompound.csv')
colnames(WellNameCompound)
colnames(replicates_average_mean_normalized)
replicates_average_mean_normalized_compounds<- replicates_average_mean_normalized%>%full_join(WellNameCompound, by = "WellName_R1")




# Exporting the file for heat map and analysis

write.csv(replicates_1_mean_normalized, "Output/HBEC_Freq_Replicate1.csv", row.names=FALSE)
write.csv(replicates_2_mean_normalized, "Output/HBEC_Freq_Replicate2.csv", row.names=FALSE)
write.csv(replicates_average_mean_normalized_compounds, "Output/HBEC_Freq.csv", row.names = FALSE)


sum(is.na(replicates_average_mean_normalized_compounds))
sum(is.na(replicates_1_mean_normalized))
sum(is.na(replicates_2_mean_normalized))


```


Input: HBEC_Freq.csv 
Output: CSV file with line 22 and 98 removed that had no compound and compounds class added to the data 

Generating frequency with Class columns
```{r}
data1 <- read.csv("Output/HBEC_Freq.csv", comment.char="#")

#adding classes and ordering the data frame

class_compound<- read.csv("Metadata/Epi_Data_HBEC_Class.csv")
class_compound<-class_compound[c(1,2)] 
data1 <-data1%>% filter(!row_number() %in% c(22,98))    # removing the blank column separately 
class_compound <-class_compound%>% filter(!row_number() %in% c(22,98)) # removing the blank column separately 
data1<-cbind( class_compound,data1 ) # was not able to remoce row 22 and 98 after combining
 # removing the second reduntant compound column 19

data1<- data1[-c(19)]
colnames(data1)
sorted_class<-data1[with(data1, order(Class, Compound)),]
colnames(sorted_class)
write.csv(sorted_class, "Output/HBEC_Freq_Class_Sorted_22_98-removed.csv", row.names = FALSE)


```


                    Using this module for the final figure. 

Input: HBEC_Freq.csv file from line 706 that has NA changed to "20"
Output: Heat map with 
        a. Sorted compound
        b. ascending gene order
        c NA left white
```{r}
sorted_class <- read.csv("Output/HBEC_Freq_Class_Sorted_22_98-removed.csv", comment.char="#")# row 22 already removed
colnames(sorted_class)

rnames <- sorted_class[,2]                            # assign labels in column 1 to "rnames"
mat_data <- data.matrix(sorted_class[,5:18])  # transform column 3-5 into a matrix
rownames(mat_data) <- rnames  

my_palette <- colorRampPalette(c("red", "cornsilk", "blue"))(n = 299)


col_breaks = c(seq(.001,0.5,length=100),  # for red
               seq(0.51,1.5,length=100),  # for yellow
               seq(1.51,3,length=100))   #blue
              

heatmap.2(mat_data, 
           lhei = c(2,12),
           main = "HBEC_freq",
           margin=c(10,12),
          cexRow = .2,
           col= my_palette,
           breaks = col_breaks,
           trace = "none",
           dendrogram="none",
          density.info="none",
          
          Colv=FALSE, Rowv=FALSE)# for non clustered heat map



#For heat map with class of compound

sorted_class <- read.csv("HBEC_Freq_Class_Sorted_NA20_22_98-removed.csv", comment.char="#")# row 22 already removed
colnames(sorted_class)
rnames <- sorted_class[,1]                            # assign labels in column 1 to "rnames"
mat_data <- data.matrix(sorted_class[,5:18])  # transform column 3-5 into a matrix
rownames(mat_data) <- rnames  
#print(head(mat_data))


my_palette <- colorRampPalette(c("red", "cornsilk", "blue"))(n = 299)


col_breaks = c(seq(.001,0.5,length=100),  # for red
               seq(0.51,1.5,length=100),  # for yellow
               seq(1.51,3,length=100))    #blue
                    # for black

heatmap.2(mat_data, 
           lhei = c(2,12),
           main = "HBEC_Freq",
           margin=c(10,12),
          cexRow = .5,
           col= my_palette,
           breaks = col_breaks,
           trace = "none",
           dendrogram="none",
          density.info="none",
          
          Colv=FALSE, Rowv=FALSE)# for non clustered heat maps










```
