---
title: "ClassAndOverall_changes"
author: "Varun"
date: "2/7/2023"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Using the bursting data for MCF7 generated in figure 2B 2C and 2D

```{r}
library(readr)
library (dplyr)
library(ggplot2)
library(plyr)
library(tidyverse)
library(knitr)
library(SpatialTools)
library(reshape2)
library(data.table)
library(tidyr)
library(RColorBrewer)
library(gplots)
library(ggbreak)
library(patchwork)

library(RColorBrewer)
library(viridis)
library(readr)
library (dplyr)
library(ggplot2)
library(plyr)
library(tidyverse)
library(knitr)
library(SpatialTools)
library(reshape2)
library(data.table)
library(tidyr)
library(RColorBrewer)
library(gplots)
library(ggprism)

```

 Reading tables and attaching the class

```{r}
## Preparing averaged and replicate files for  freq int and het
########################################### Freq###########

Freq12<-read.csv(file= 'Metadata/MCF7_Freq.csv')
Freq1<-read.csv(file= 'Metadata/MCF7_Freq_Replicate1.csv')
Freq2<-read.csv(file= 'Metadata/MCF7_Freq_Replicate2.csv')
Freq_untreated<- read.csv(file= 'Metadata/MCF7_Freq_Untreated.csv')
colnames(Freq12)
colnames(Freq12)[c(17)]<-"typo.compounds"
colnames(Freq1)[c(1)]<-"WellName_R1"
colnames(Freq2)[c(1)]<-"WellName_R2"
## getting the compound and class addred to average file
class_compound<- read.csv("Epi_Data_HBEC_Class.csv")
class_compound<-class_compound[c(1,2)]  
Freq12<-cbind( class_compound,Freq12 ) # used cbind instead of full join with compounds as reference since compounds in the Int 12 file had wierd characters after export
# adding class and compound to replicates
R1<-Freq12[c(1,2,3)]
R2<-Freq12[c(1,2,4)]
Freq1<-Freq1%>%full_join(R1, by = "WellName_R1")
Freq2<-Freq2%>%full_join(R2, by = "WellName_R2")
# colnames(Freq1)[c(9)]<-"Nras"
# colnames(Freq2)[c(9)]<-"Nras"
Freq12 <-Freq12%>% filter(!row_number() %in% c(22,98)) 
Freq1 <-Freq1 %>% filter(!row_number() %in% c(22,98)) 
Freq2  <-Freq2 %>% filter(!row_number() %in% c(22,98)) 


########################################### INT  ###########

Int12<-read.csv(file= 'Metadata/MCF7_Int.csv')
Int1<-read.csv(file= 'Metadata/MCF7_Int_Replicate1.csv')
Int2<-read.csv(file= 'Metadata/MCF7_Int_Replicate2.csv')
Int_untreated<- read.csv(file= 'Metadata/MCF7_Int_Untreated.csv')
Int_untreated<-  Int_untreated[c(-1)]  # removing idex row
colnames(Int12)
colnames(Int12)[c(17)]<-"typo.compounds"
colnames(Int1)[c(1)]<-"WellName_R1"
colnames(Int2)[c(1)]<-"WellName_R2"
## getting the compound and class addred to average file
class_compound<- read.csv("Epi_Data_HBEC_Class.csv")
class_compound<-class_compound[c(1,2)]  
Int12<-cbind( class_compound,Int12 ) # used cbind since 8 compounds in the Int 12 file had wierd characters
# adding class and compound to replicates
R1<-Int12[c(1,2,3)]
R2<-Int12[c(1,2,4)]
Int1<-Int1%>%full_join(R1, by = "WellName_R1")
Int2<-Int2%>%full_join(R2, by = "WellName_R2")

Int12 <-Int12%>% filter(!row_number() %in% c(22,98)) 
Int1 <-Int1 %>% filter(!row_number() %in% c(22,98)) 
Int2  <-Int2 %>% filter(!row_number() %in% c(22,98)) 

########################################### HET  ###########

Het12<-read.csv(file= 'Metadata/MCF7_Het.csv')
Het1<-read.csv(file= 'Metadata/MCF7_Het_Replicate1.csv')
Het2<-read.csv(file= 'Metadata/MCF7_Het_Replicate2.csv')
Het_untreated<- read.csv(file= 'Metadata/MCF7_Het_Untreated.csv')
Het_untreated<-  Het_untreated[c(-1)]  # removing idex row
colnames(Int12)
colnames(Het12)
colnames(Het12)[c(17)]<-"typo.compounds"
colnames(Het1)[c(1)]<-"WellName_R1"
colnames(Het2)[c(1)]<-"WellName_R2"
## getting the compound and class addred to average file
class_compound<- read.csv("Epi_Data_HBEC_Class.csv")
class_compound<-class_compound[c(1,2)]  
Het12<-cbind( class_compound,Het12 ) # used cbind since 8 compounds in the Int 12 file had wierd characters
# adding class and compound to replicates
R1<-Het12[c(1,2,3)]
R2<-Het12[c(1,2,4)]
Het1<-Het1%>%full_join(R1, by = "WellName_R1")
Het2<-Het2%>%full_join(R2, by = "WellName_R2")


Het12 <-Het12%>% filter(!row_number() %in% c(22,98)) 
Het1 <-Het1 %>% filter(!row_number() %in% c(22,98)) 
Het2  <-Het2 %>% filter(!row_number() %in% c(22,98)) 

# freq<- freq1[c(3:16)]
# int<-int1[c(3:16)]
# het<-het1[c(3:16)]
```

For Figure 2B: 

 Calculating the absolute value of change for the freq int  for comparison with the untreated
MCF7_Freq_NativeVSMean.csv
MCF7_Int_NativeVSMean.csv

```{r}

########################################### MOD change FREQ  ##################################################################################


# getting the absolute change and the mean for freq1 and 2, transposing , then renaming the columns to gene names

Mean_Abs_dFreq1<- Freq1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Absolute_Canx=abs(Canx-1), 
                                                                      Absolute_Dnajc5=abs(Dnajc5-1),
                                                                      Absolute_Egfr=abs(Egfr-1),
                                                                      Absolute_Errfi1=abs(Errfi1-1),
                                                                      Absolute_Gapdh=abs(Gapdh-1),
                                                                      Absolute_Kpnb1=abs(Kpnb1-1),
                                                                      Absolute_Myc=abs(Myc-1),
                                                                      Absolute_Nras=abs(Nras-1),
                                                                      Absolute_P53=abs(P53-1),
                                                                      Absolute_Rab7a=abs(Rab7a-1),
                                                                      Absolute_RhoA=abs(RhoA-1),
                                                                      Absolute_Rpap3=abs(Rpap3-1),
                                                                      Absolute_Sec16a=abs(Sec16a-1),
                                                                      Absolute_Slc2a1=abs(Slc2a1-1)
                                                                      )%>%
                                                                      summarise(Canx=mean(Absolute_Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Absolute_Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Absolute_Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Absolute_Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Absolute_Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Absolute_Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Absolute_Myc, na.rm = TRUE),
                                                                      Nras=mean(Absolute_Nras, na.rm = TRUE),
                                                                      P53=mean(Absolute_P53, na.rm = TRUE),
                                                                      Rab7a=mean(Absolute_Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(Absolute_RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Absolute_Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Absolute_Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Absolute_Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_dFre2=V1)%>%select(c(-1))



Mean_Abs_dFreq2<- Freq2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Absolute_Canx=abs(Canx-1), 
                                                                      Absolute_Dnajc5=abs(Dnajc5-1),
                                                                      Absolute_Egfr=abs(Egfr-1),
                                                                      Absolute_Errfi1=abs(Errfi1-1),
                                                                      Absolute_Gapdh=abs(Gapdh-1),
                                                                      Absolute_Kpnb1=abs(Kpnb1-1),
                                                                      Absolute_Myc=abs(Myc-1),
                                                                      Absolute_Nras=abs(Nras-1),
                                                                      Absolute_P53=abs(P53-1),
                                                                      Absolute_Rab7a=abs(Rab7a-1),
                                                                      Absolute_RhoA=abs(RhoA-1),
                                                                      Absolute_Rpap3=abs(Rpap3-1),
                                                                      Absolute_Sec16a=abs(Sec16a-1),
                                                                      Absolute_Slc2a1=abs(Slc2a1-1)
                                                                      )%>%
                                                                      summarise(Canx=mean(Absolute_Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Absolute_Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Absolute_Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Absolute_Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Absolute_Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Absolute_Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Absolute_Myc, na.rm = TRUE),
                                                                      Nras=mean(Absolute_Nras, na.rm = TRUE),
                                                                      P53=mean(Absolute_P53, na.rm = TRUE),
                                                                      Rab7a=mean(Absolute_Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(Absolute_RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Absolute_Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Absolute_Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Absolute_Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_dFre2=V1)%>%select(c(-1))



# calculating the mean and SE of the untreated smaples

Mean_Untreated_Freq<-Freq_untreated%>% summarise(Canx=mean(Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Myc, na.rm = TRUE),
                                                                      Nras=mean(Nras, na.rm = TRUE),
                                                                      P53=mean(P53, na.rm = TRUE),
                                                                      Rab7a=mean(Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_Mean_Ctrl_freq=V1)%>%select(c(-1))

SD_Untreated_Freq<-Freq_untreated%>% summarise(Canx=sd(Canx, na.rm = TRUE), 
                                                                      Dnajc5=sd(Dnajc5, na.rm = TRUE),
                                                                      Egfr=sd(Egfr, na.rm = TRUE),
                                                                      Errfi1=sd(Errfi1, na.rm = TRUE),
                                                                      Gapdh=sd(Gapdh, na.rm = TRUE),
                                                                      Kpnb1=sd(Kpnb1, na.rm = TRUE),
                                                                      Myc=sd(Myc, na.rm = TRUE),
                                                                      Nras=sd(Nras, na.rm = TRUE),
                                                                      P53=sd(P53, na.rm = TRUE),
                                                                      Rab7a=sd(Rab7a , na.rm = TRUE),
                                                                      RhoA=sd(RhoA, na.rm = TRUE),
                                                                      Rpap3=sd(Rpap3, na.rm = TRUE),
                                                                      Sec16a=sd(Sec16a, na.rm = TRUE),
                                                                      Slc2a1=sd(Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_SD_Ctrl_Freq=V1)%>%select(c(-1))
  
  
Samples_Untreated_Freq <-colSums(!is.na(Freq_untreated[c(-1)]))%>% as.data.frame()
colnames(Samples_Untreated_Freq)<-"Sample_number"
SE_untreated_Freq<- cbind(SD_Untreated_Freq,Samples_Untreated_Freq)






SE_untreated_Freq<- cbind(SD_Untreated_Freq,Samples_Untreated_Freq)%>%mutate(SE_MCF7_Ctrl = MCF7_SD_Ctrl_Freq/sqrt(Sample_number))%>%select(c(3))

                            
                                                                        
                                               
MCF7_freq_Native_ModCHange<-cbind(Mean_Untreated_Freq,SE_untreated_Freq,Mean_Abs_dFreq1,Mean_Abs_dFreq2)

write.csv(MCF7_freq_Native_ModCHange, 'Output/MCF7_Freq_NativeVSMean.csv')







########################################### MOD change INT  ##################################################################################

# getting the absolute change and the mean for freq1 and 2, transposing , then renaming the columns to gene names

Mean_Abs_dInt1<- Int1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Absolute_Canx=abs(Canx-1), 
                                                                      Absolute_Dnajc5=abs(Dnajc5-1),
                                                                      Absolute_Egfr=abs(Egfr-1),
                                                                      Absolute_Errfi1=abs(Errfi1-1),
                                                                      Absolute_Gapdh=abs(Gapdh-1),
                                                                      Absolute_Kpnb1=abs(Kpnb1-1),
                                                                      Absolute_Myc=abs(Myc-1),
                                                                      Absolute_Nras=abs(Nras-1),
                                                                      Absolute_P53=abs(P53-1),
                                                                      Absolute_Rab7a=abs(Rab7a-1),
                                                                      Absolute_RhoA=abs(RhoA-1),
                                                                      Absolute_Rpap3=abs(Rpap3-1),
                                                                      Absolute_Sec16a=abs(Sec16a-1),
                                                                      Absolute_Slc2a1=abs(Slc2a1-1)
                                                                      )%>%
                                                                      summarise(Canx=mean(Absolute_Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Absolute_Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Absolute_Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Absolute_Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Absolute_Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Absolute_Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Absolute_Myc, na.rm = TRUE),
                                                                      Nras=mean(Absolute_Nras, na.rm = TRUE),
                                                                      P53=mean(Absolute_P53, na.rm = TRUE),
                                                                      Rab7a=mean(Absolute_Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(Absolute_RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Absolute_Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Absolute_Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Absolute_Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_dInt1=V1)%>%select(c(-1))



Mean_Abs_dInt2<- Int2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Absolute_Canx=abs(Canx-1), 
                                                                      Absolute_Dnajc5=abs(Dnajc5-1),
                                                                      Absolute_Egfr=abs(Egfr-1),
                                                                      Absolute_Errfi1=abs(Errfi1-1),
                                                                      Absolute_Gapdh=abs(Gapdh-1),
                                                                      Absolute_Kpnb1=abs(Kpnb1-1),
                                                                      Absolute_Myc=abs(Myc-1),
                                                                      Absolute_Nras=abs(Nras-1),
                                                                      Absolute_P53=abs(P53-1),
                                                                      Absolute_Rab7a=abs(Rab7a-1),
                                                                      Absolute_RhoA=abs(RhoA-1),
                                                                      Absolute_Rpap3=abs(Rpap3-1),
                                                                      Absolute_Sec16a=abs(Sec16a-1),
                                                                      Absolute_Slc2a1=abs(Slc2a1-1)
                                                                      )%>%
                                                                      summarise(Canx=mean(Absolute_Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Absolute_Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Absolute_Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Absolute_Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Absolute_Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Absolute_Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Absolute_Myc, na.rm = TRUE),
                                                                      Nras=mean(Absolute_Nras, na.rm = TRUE),
                                                                      P53=mean(Absolute_P53, na.rm = TRUE),
                                                                      Rab7a=mean(Absolute_Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(Absolute_RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Absolute_Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Absolute_Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Absolute_Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_dInt2=V1)%>%select(c(-1))



# calculating the mean and SE of the untreated smaples

Mean_Untreated_Int<-Int_untreated%>% summarise(Canx=mean(Canx, na.rm = TRUE), 
                                                                      Dnajc5=mean(Dnajc5, na.rm = TRUE),
                                                                      Egfr=mean(Egfr, na.rm = TRUE),
                                                                      Errfi1=mean(Errfi1, na.rm = TRUE),
                                                                      Gapdh=mean(Gapdh, na.rm = TRUE),
                                                                      Kpnb1=mean(Kpnb1, na.rm = TRUE),
                                                                      Myc=mean(Myc, na.rm = TRUE),
                                                                      Nras=mean(Nras, na.rm = TRUE),
                                                                      P53=mean(P53, na.rm = TRUE),
                                                                      Rab7a=mean(Rab7a , na.rm = TRUE),
                                                                      RhoA=mean(RhoA, na.rm = TRUE),
                                                                      Rpap3=mean(Rpap3, na.rm = TRUE),
                                                                      Sec16a=mean(Sec16a, na.rm = TRUE),
                                                                      Slc2a1=mean(Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_Mean_Ctrl_Int=V1)%>%select(c(-1))

SD_Untreated_Int<-Int_untreated%>% summarise(Canx=sd(Canx, na.rm = TRUE), 
                                                                      Dnajc5=sd(Dnajc5, na.rm = TRUE),
                                                                      Egfr=sd(Egfr, na.rm = TRUE),
                                                                      Errfi1=sd(Errfi1, na.rm = TRUE),
                                                                      Gapdh=sd(Gapdh, na.rm = TRUE),
                                                                      Kpnb1=sd(Kpnb1, na.rm = TRUE),
                                                                      Myc=sd(Myc, na.rm = TRUE),
                                                                      Nras=sd(Nras, na.rm = TRUE),
                                                                      P53=sd(P53, na.rm = TRUE),
                                                                      Rab7a=sd(Rab7a , na.rm = TRUE),
                                                                      RhoA=sd(RhoA, na.rm = TRUE),
                                                                      Rpap3=sd(Rpap3, na.rm = TRUE),
                                                                      Sec16a=sd(Sec16a, na.rm = TRUE),
                                                                      Slc2a1=sd(Slc2a1, na.rm = TRUE)
                                                                      )%>%
t()%>% as.data.frame()%>%mutate(MCF7_SD_Ctrl_Int=V1)%>%select(c(-1))
  
  
Samples_Untreated_Int <-colSums(!is.na(Int_untreated[c(-1)]))%>% as.data.frame()
colnames(Samples_Untreated_Int)<-"Sample_number"
SE_untreated_Int<- cbind(SD_Untreated_Int,Samples_Untreated_Int)






SE_untreated_Int<- cbind(SD_Untreated_Int,Samples_Untreated_Int)%>%mutate(SE_MCF7_Ctrl = MCF7_SD_Ctrl_Int/sqrt(Sample_number))%>%select(c(3))

                            
                                                                        
                                               
MCF7_Int_Native_ModCHange<-cbind(Mean_Untreated_Int,SE_untreated_Int,Mean_Abs_dInt1,Mean_Abs_dInt2)

write.csv(MCF7_Int_Native_ModCHange, 'Output/MCF7_Int_NativeVSMean.csv')



```

FOR FIGURE 2C, 3C and S7C

Calculating the change by subtracting 1 and taking the mod to get the average change per compound class for freq het and int 
MCF7_mod_class_average_freq_int_het.csv


```{r}
                                                                                                                      ############# frequency #################
Mod_MCF7_freq<- Freq12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx_F-1)), 
                                                                      Dnajc5=(abs(Dnajc5_F-1)),
                                                                      Egfr=(abs(Egfr_F-1)),
                                                                      Errfi1=(abs(Errfi1_F-1)),
                                                                      Gapdh=(abs(Gapdh_F-1)),
                                                                      Kpnb1=(abs(Kpnb1_F-1)),
                                                                      Myc=(abs(Myc_F-1)),
                                                                      Nras=(abs(Nras_F-1)),
                                                                      P53=(abs(P53_F-1)),
                                                                      Rab7a=(abs(Rab7a_F-1)),
                                                                      RhoA=(abs(RhoA_F-1)),
                                                                      Rpap3=(abs(Rpap3_F-1)),
                                                                      Sec16a=(abs(Sec16a_F-1)),
                                                                      Slc2a1=(abs(Slc2a1_F-1)))
                                                                      

Mod_MCF7_freq_1<- Freq1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx-1)), 
                                                                      Dnajc5=(abs(Dnajc5-1)),
                                                                      Egfr=(abs(Egfr-1)),
                                                                      Errfi1=(abs(Errfi1-1)),
                                                                      Gapdh=(abs(Gapdh-1)),
                                                                      Kpnb1=(abs(Kpnb1-1)),
                                                                      Myc=(abs(Myc-1)),
                                                                      Nras=(abs(Nras-1)),
                                                                      P53=(abs(P53-1)),
                                                                      Rab7a=(abs(Rab7a-1)),
                                                                      RhoA=(abs(RhoA-1)),
                                                                      Rpap3=(abs(Rpap3-1)),
                                                                      Sec16a=(abs(Sec16a-1)),
                                                                      Slc2a1=(abs(Slc2a1-1)))


Mod_MCF7_freq_2<- Freq2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx-1)), 
                                                                      Dnajc5=(abs(Dnajc5-1)),
                                                                      Egfr=(abs(Egfr-1)),
                                                                      Errfi1=(abs(Errfi1-1)),
                                                                      Gapdh=(abs(Gapdh-1)),
                                                                      Kpnb1=(abs(Kpnb1-1)),
                                                                      Myc=(abs(Myc-1)),
                                                                      Nras=(abs(Nras-1)),
                                                                      P53=(abs(P53-1)),
                                                                      Rab7a=(abs(Rab7a-1)),
                                                                      RhoA=(abs(RhoA-1)),
                                                                      Rpap3=(abs(Rpap3-1)),
                                                                      Sec16a=(abs(Sec16a-1)),
                                                                      Slc2a1=(abs(Slc2a1-1)))







                                                                                                                                ##################### Int  ##################

Mod_MCF7_int<- Int12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx_I-1)), 
                                                                      Dnajc5=(abs(Dnajc5_I-1)),
                                                                      Egfr=(abs(Egfr_I-1)),
                                                                      Errfi1=(abs(Errfi1_I-1)),
                                                                      Gapdh=(abs(Gapdh_I-1)),
                                                                      Kpnb1=(abs(Kpnb1_I-1)),
                                                                      Myc=(abs(Myc_I-1)),
                                                                      Nras=(abs(Nras_I-1)),
                                                                      P53=(abs(P53_I-1)),
                                                                      Rab7a=(abs(Rab7a_I-1)),
                                                                      RhoA=(abs(RhoA_I-1)),
                                                                      Rpap3=(abs(Rpap3_I-1)),
                                                                      Sec16a=(abs(Sec16a_I-1)),
                                                                      Slc2a1=(abs(Slc2a1_I-1))
                                                                      )


Mod_MCF7_int_1<- Int1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx-1)), 
                                                                      Dnajc5=(abs(Dnajc5-1)),
                                                                      Egfr=(abs(Egfr-1)),
                                                                      Errfi1=(abs(Errfi1-1)),
                                                                      Gapdh=(abs(Gapdh-1)),
                                                                      Kpnb1=(abs(Kpnb1-1)),
                                                                      Myc=(abs(Myc-1)),
                                                                      Nras=(abs(Nras-1)),
                                                                      P53=(abs(P53-1)),
                                                                      Rab7a=(abs(Rab7a-1)),
                                                                      RhoA=(abs(RhoA-1)),
                                                                      Rpap3=(abs(Rpap3-1)),
                                                                      Sec16a=(abs(Sec16a-1)),
                                                                      Slc2a1=(abs(Slc2a1-1))
                                                                      )



Mod_MCF7_int_2<- Int2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(abs(Canx-1)), 
                                                                      Dnajc5=(abs(Dnajc5-1)),
                                                                      Egfr=(abs(Egfr-1)),
                                                                      Errfi1=(abs(Errfi1-1)),
                                                                      Gapdh=(abs(Gapdh-1)),
                                                                      Kpnb1=(abs(Kpnb1-1)),
                                                                      Myc=(abs(Myc-1)),
                                                                      Nras=(abs(Nras-1)),
                                                                      P53=(abs(P53-1)),
                                                                      Rab7a=(abs(Rab7a-1)),
                                                                      RhoA=(abs(RhoA-1)),
                                                                      Rpap3=(abs(Rpap3-1)),
                                                                      Sec16a=(abs(Sec16a-1)),
                                                                      Slc2a1=(abs(Slc2a1-1))
                                                                      )







##################### Het  ##################




Mod_MCF7_het<- Het12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Mod(Canx_H-1)), 
                                                                      Dnajc5=(Mod(Dnajc5_H-1)),
                                                                      Egfr=(Mod(Egfr_H-1)),
                                                                      Errfi1=(Mod(Errfi1_H-1)),
                                                                      Gapdh=(Mod(Gapdh_H-1)),
                                                                      Kpnb1=(Mod(Kpnb1_H-1)),
                                                                      Myc=(Mod(Myc_H-1)),
                                                                      Nras=(Mod(Nras_H-1)),
                                                                      P53=(Mod(P53_H-1)),
                                                                      Rab7a=(Mod(Rab7a_H-1)),
                                                                      RhoA=(Mod(RhoA_H-1)),
                                                                      Rpap3=(Mod(Rpap3_H-1)),
                                                                      Sec16a=(Mod(Sec16a_H-1)),
                                                                      Slc2a1=(Mod(Slc2a1_H-1))

)

Mod_MCF7_het_1<- Het1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Mod(Canx-1)), 
                                                                      Dnajc5=(Mod(Dnajc5-1)),
                                                                      Egfr=(Mod(Egfr-1)),
                                                                      Errfi1=(Mod(Errfi1-1)),
                                                                      Gapdh=(Mod(Gapdh-1)),
                                                                      Kpnb1=(Mod(Kpnb1-1)),
                                                                      Myc=(Mod(Myc-1)),
                                                                      Nras=(Mod(Nras-1)),
                                                                      P53=(Mod(P53-1)),
                                                                      Rab7a=(Mod(Rab7a-1)),
                                                                      RhoA=(Mod(RhoA-1)),
                                                                      Rpap3=(Mod(Rpap3-1)),
                                                                      Sec16a=(Mod(Sec16a-1)),
                                                                      Slc2a1=(Mod(Slc2a1-1))

)

Mod_MCF7_het_2<- Het2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Mod(Canx-1)), 
                                                                      Dnajc5=(Mod(Dnajc5-1)),
                                                                      Egfr=(Mod(Egfr-1)),
                                                                      Errfi1=(Mod(Errfi1-1)),
                                                                      Gapdh=(Mod(Gapdh-1)),
                                                                      Kpnb1=(Mod(Kpnb1-1)),
                                                                      Myc=(Mod(Myc-1)),
                                                                      Nras=(Mod(Nras-1)),
                                                                      P53=(Mod(P53-1)),
                                                                      Rab7a=(Mod(Rab7a-1)),
                                                                      RhoA=(Mod(RhoA-1)),
                                                                      Rpap3=(Mod(Rpap3-1)),
                                                                      Sec16a=(Mod(Sec16a-1)),
                                                                      Slc2a1=(Mod(Slc2a1-1))

)










############ averaging the Absolute values of mean change classwise ##############

Cell_line<-replicate(7,rep("MCF7"))

freq_long_1 <- Mod_MCF7_freq_1%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_freq") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(freq_mean1 = mean (change_freq, na.rm = TRUE))


freq_long_2 <- Mod_MCF7_freq_2%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_freq") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(freq_mean2 = mean (change_freq, na.rm = TRUE))





int_long_1 <- Mod_MCF7_int_1%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_int") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(int_mean1 = mean (change_int, na.rm = TRUE))


int_long_2 <- Mod_MCF7_int_2%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_int") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(int_mean2 = mean (change_int, na.rm = TRUE))




het_long_1 <- Mod_MCF7_het_1%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_het") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(het_mean1 = mean (change_het, na.rm = TRUE))


het_long_2 <- Mod_MCF7_het_2%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_het") %>% 
  filter(Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'))%>%
  as.tibble()%>%
  group_by(Class)%>%
  dplyr:::summarize(het_mean2 = mean (change_het, na.rm = TRUE))


### Combining and writing the csv


MCF7_freq1n2<-  freq_long_1%>%left_join(freq_long_2, by = "Class")%>%cbind(Cell_line) 
MCF7_int1n2<-  int_long_1%>%left_join(int_long_2, by = "Class")%>%cbind(Cell_line) 
MCF7_het1n2<-  het_long_1%>%left_join(het_long_2, by = "Class")%>%cbind(Cell_line) 
MCF7_class_all_mod <- cbind(MCF7_freq1n2, MCF7_int1n2, MCF7_het1n2)

write.csv(MCF7_class_all_mod, "Output/MCF7_mod_class_average_freq_int_het.csv")


```



Figure 2D, 3D and S7D

Calculating the change by subtracting 1 and plotting classwise relative change as box plot

```{r}


############# frequency #################
NoMod_MCF7_freq<- Freq12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_F-1), 
                                                                      Dnajc5=(Dnajc5_F-1),
                                                                      Egfr=(Egfr_F-1),
                                                                      Errfi1=(Errfi1_F-1),
                                                                      Gapdh=(Gapdh_F-1),
                                                                      Kpnb1=(Kpnb1_F-1),
                                                                      Myc=(Myc_F-1),
                                                                      Nras=(Nras_F-1),
                                                                      P53=(P53_F-1),
                                                                      Rab7a=(Rab7a_F-1),
                                                                      RhoA=(RhoA_F-1),
                                                                      Rpap3=(Rpap3_F-1),
                                                                      Sec16a=(Sec16a_F-1),
                                                                      Slc2a1=(Slc2a1_F-1)
                                                                      )

NoMod_MCF7_freq_1<- Freq1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )

NoMod_MCF7_freq_2<- Freq2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )


##################### Int  ##################

NoMod_MCF7_int<- Int12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_I-1), 
                                                                      Dnajc5=(Dnajc5_I-1),
                                                                      Egfr=(Egfr_I-1),
                                                                      Errfi1=(Errfi1_I-1),
                                                                      Gapdh=(Gapdh_I-1),
                                                                      Kpnb1=(Kpnb1_I-1),
                                                                      Myc=(Myc_I-1),
                                                                      Nras=(Nras_I-1),
                                                                      P53=(P53_I-1),
                                                                      Rab7a=(Rab7a_I-1),
                                                                      RhoA=(RhoA_I-1),
                                                                      Rpap3=(Rpap3_I-1),
                                                                      Sec16a=(Sec16a_I-1),
                                                                      Slc2a1=(Slc2a1_I-1)
                                                                      )


NoMod_MCF7_int_1<- Int1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )



NoMod_MCF7_int_2<- Int2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )







##################### Het  ##################




NoMod_MCF7_het<- Het12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_H-1), 
                                                                      Dnajc5=(Dnajc5_H-1),
                                                                      Egfr=(Egfr_H-1),
                                                                      Errfi1=(Errfi1_H-1),
                                                                      Gapdh=(Gapdh_H-1),
                                                                      Kpnb1=(Kpnb1_H-1),
                                                                      Myc=(Myc_H-1),
                                                                      Nras=(Nras_H-1),
                                                                      P53=(P53_H-1),
                                                                      Rab7a=(Rab7a_H-1),
                                                                      RhoA=(RhoA_H-1),
                                                                      Rpap3=(Rpap3_H-1),
                                                                      Sec16a=(Sec16a_H-1),
                                                                      Slc2a1=(Slc2a1_H-1)

)

NoMod_MCF7_het_1<- Het1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)

)

NoMod_MCF7_het_2<- Het2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)

)



########################### Freq    ########

colnames(NoMod_MCF7_freq_1)
colnames(NoMod_MCF7_freq_2)

# removing compound names
NoMod_MCF7_freq_1<-NoMod_MCF7_freq_1[c(-2)]
NoMod_MCF7_freq_2<-NoMod_MCF7_freq_2[c(-2)]


# pivotting long and selecting class

NoMod_MCF7_freq_1_long <- NoMod_MCF7_freq_1%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_freq")
NoMod_MCF7_freq_1_long_class<-NoMod_MCF7_freq_1_long[NoMod_MCF7_freq_1_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]


NoMod_MCF7_freq_2_long <- NoMod_MCF7_freq_2%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_freq")
NoMod_MCF7_freq_2_long_class<-NoMod_MCF7_freq_2_long[NoMod_MCF7_freq_2_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]


# generating column for replicate

Rep1<-replicate(1638,rep("#1"))
Rep2<-replicate(1638,rep("#2"))

NoMod_MCF7_freq_1_long_class<-cbind(NoMod_MCF7_freq_1_long_class, Rep1)
NoMod_MCF7_freq_2_long_class<-cbind(NoMod_MCF7_freq_2_long_class, Rep2)

colnames(NoMod_MCF7_freq_1_long_class)[c(4)]<-"Replicate"
colnames(NoMod_MCF7_freq_2_long_class)[c(4)]<-"Replicate"


NoMod_MCF7_freq_long_class_12<-rbind(NoMod_MCF7_freq_1_long_class, NoMod_MCF7_freq_2_long_class)



 ggplot(data= NoMod_MCF7_freq_long_class_12, aes(y=change_freq, x = Class, color= Replicate)) +
  #geom_point(aes(color=Class), alpha=.6, position = position_jitterdodge(jitter.width = 0.25))
  geom_jitter(aes(color=Class), alpha=.7)+
  geom_boxplot(outlier.shape = NA, alpha = 0)+
  scale_color_prism("prism_dark2")+
  theme_prism()+
  #theme_bw() + 
  theme(axis.text.x = element_text(size = 10), axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14), axis.title.y = element_text(size = 16),
        plot.title = element_text(size = 18, face = "bold", color = "Black", hjust = 0.5),
        panel.border = element_blank(),
        panel.background = element_rect(fill = "White"))+
        labs(fill="")+
        labs(title = "Classwise burst frequency changes: MCF7", x = "Inhibitor classes", y = "Relative burst frequency") +
ylim(-1,1)
  







########################### Int   ########


colnames(NoMod_MCF7_int_1)
colnames(NoMod_MCF7_int_2)

# removing compound names
NoMod_MCF7_int_1<-NoMod_MCF7_int_1[c(-2)]
NoMod_MCF7_int_2<-NoMod_MCF7_int_2[c(-2)]




NoMod_MCF7_int_1_long <- NoMod_MCF7_int_1%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_int")
NoMod_MCF7_int_1_long_class<-NoMod_MCF7_int_1_long[NoMod_MCF7_int_1_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]


NoMod_MCF7_int_2_long <- NoMod_MCF7_int_2%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_int")
NoMod_MCF7_int_2_long_class<-NoMod_MCF7_int_2_long[NoMod_MCF7_int_2_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]



Rep1<-replicate(1638,rep("#1"))
Rep2<-replicate(1638,rep("#2"))

NoMod_MCF7_int_1_long_class<-cbind(NoMod_MCF7_int_1_long_class, Rep1)
NoMod_MCF7_int_2_long_class<-cbind(NoMod_MCF7_int_2_long_class, Rep2)

colnames(NoMod_MCF7_int_1_long_class)[c(4)]<-"Replicate"
colnames(NoMod_MCF7_int_2_long_class)[c(4)]<-"Replicate"


NoMod_MCF7_int_long_class_12<-rbind(NoMod_MCF7_int_1_long_class, NoMod_MCF7_int_2_long_class)


######## 
# ggplot(data= NoMod_MCF7_int_long_class_12, aes(y=change_int, x = Class, fill= Replicate)) + geom_violin()+
 ggplot(data= NoMod_MCF7_int_long_class_12, aes(y=change_int, x = Class, color= Replicate)) +geom_jitter(aes(color=Class), alpha=.7)+
geom_boxplot(outlier.shape = NA, alpha = 0)+
  scale_color_prism("prism_dark2")+
  theme_prism()+
  #theme_bw() +  
  theme(axis.text.x = element_text(size = 10), axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14), axis.title.y = element_text(size = 16),
        plot.title = element_text(size = 18, face = "bold", color = "Black", hjust = 0.5),
        panel.border = element_blank(),
        panel.background = element_rect(fill = "White"))+
        labs(fill="")+
        labs(title = "Classwise burst size changes: MCF7", x = "Inhibitor classes", y = "Relative burst size")+
ylim(-.5,.5)





########################### Het   ########


colnames(NoMod_MCF7_het_1)
colnames(NoMod_MCF7_het_2)

# removing compound names
NoMod_MCF7_het_1<-NoMod_MCF7_het_1[c(-2)]
NoMod_MCF7_het_2<-NoMod_MCF7_het_2[c(-2)]




NoMod_MCF7_het_1_long <- NoMod_MCF7_het_1%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_het")
NoMod_MCF7_het_1_long_class<-NoMod_MCF7_het_1_long[NoMod_MCF7_het_1_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]


NoMod_MCF7_het_2_long <- NoMod_MCF7_het_2%>%pivot_longer(cols = c(2:15),
               names_to = "gene",
               values_to ="change_het")
NoMod_MCF7_het_2_long_class<-NoMod_MCF7_het_2_long[NoMod_MCF7_het_2_long$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]



Rep1<-replicate(1638,rep("#1"))
Rep2<-replicate(1638,rep("#2"))

NoMod_MCF7_het_1_long_class<-cbind(NoMod_MCF7_het_1_long_class, Rep1)
NoMod_MCF7_het_2_long_class<-cbind(NoMod_MCF7_het_2_long_class, Rep2)

colnames(NoMod_MCF7_het_1_long_class)[c(4)]<-"Replicate"
colnames(NoMod_MCF7_het_2_long_class)[c(4)]<-"Replicate"


NoMod_MCF7_het_long_class_12<-rbind(NoMod_MCF7_het_1_long_class, NoMod_MCF7_het_2_long_class)


######## 
# ggplot(data= NoMod_MCF7_het_long_class_12, aes(y=change_het, x = Class, fill= Replicate)) + geom_violin()
 ggplot(data= NoMod_MCF7_het_long_class_12, aes(y=change_het, x = Class, color= Replicate)) + geom_jitter(aes(color=Class), alpha=.7)+
  geom_boxplot(outlier.shape = NA, alpha = 0)+
  scale_color_prism("prism_dark2")+
  theme_prism()+
  #theme_bw() + 
  theme(axis.text.x = element_text(size = 10), axis.title.x = element_text(size = 16),
        axis.text.y = element_text(size = 14), axis.title.y = element_text(size = 16),
        plot.title = element_text(size = 18, face = "bold", color = "Black", hjust = 0.5),
        panel.border = element_blank(),
        panel.background = element_rect(fill = "White"))+
        labs(fill="")+
        labs(title = "Classwise heterogeneity changes: MCF7", x = "Inhibitor classes", y = "Relative heterogeneity")+
  ylim(-1,1)
    scale_y_break(c(-1,2), scale = .5)
























```

 

Figure3B and S7Bigure 3B


```{r}


############# frequency #################
NoMod_MCF7_freq<- Freq12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_F-1), 
                                                                      Dnajc5=(Dnajc5_F-1),
                                                                      Egfr=(Egfr_F-1),
                                                                      Errfi1=(Errfi1_F-1),
                                                                      Gapdh=(Gapdh_F-1),
                                                                      Kpnb1=(Kpnb1_F-1),
                                                                      Myc=(Myc_F-1),
                                                                      Nras=(Nras_F-1),
                                                                      P53=(P53_F-1),
                                                                      Rab7a=(Rab7a_F-1),
                                                                      RhoA=(RhoA_F-1),
                                                                      Rpap3=(Rpap3_F-1),
                                                                      Sec16a=(Sec16a_F-1),
                                                                      Slc2a1=(Slc2a1_F-1)
                                                                      )

NoMod_MCF7_freq_1<- Freq1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )

NoMod_MCF7_freq_2<- Freq2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )


##################### Int  ##################

NoMod_MCF7_int<- Int12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_I-1), 
                                                                      Dnajc5=(Dnajc5_I-1),
                                                                      Egfr=(Egfr_I-1),
                                                                      Errfi1=(Errfi1_I-1),
                                                                      Gapdh=(Gapdh_I-1),
                                                                      Kpnb1=(Kpnb1_I-1),
                                                                      Myc=(Myc_I-1),
                                                                      Nras=(Nras_I-1),
                                                                      P53=(P53_I-1),
                                                                      Rab7a=(Rab7a_I-1),
                                                                      RhoA=(RhoA_I-1),
                                                                      Rpap3=(Rpap3_I-1),
                                                                      Sec16a=(Sec16a_I-1),
                                                                      Slc2a1=(Slc2a1_I-1)
                                                                      )


NoMod_MCF7_int_1<- Int1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )



NoMod_MCF7_int_2<- Int2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)
                                                                      )







##################### Het  ##################




NoMod_MCF7_het<- Het12 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx_H-1), 
                                                                      Dnajc5=(Dnajc5_H-1),
                                                                      Egfr=(Egfr_H-1),
                                                                      Errfi1=(Errfi1_H-1),
                                                                      Gapdh=(Gapdh_H-1),
                                                                      Kpnb1=(Kpnb1_H-1),
                                                                      Myc=(Myc_H-1),
                                                                      Nras=(Nras_H-1),
                                                                      P53=(P53_H-1),
                                                                      Rab7a=(Rab7a_H-1),
                                                                      RhoA=(RhoA_H-1),
                                                                      Rpap3=(Rpap3_H-1),
                                                                      Sec16a=(Sec16a_H-1),
                                                                      Slc2a1=(Slc2a1_H-1)

)

NoMod_MCF7_het_1<- Het1 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)

)

NoMod_MCF7_het_2<- Het2 %>%as_tibble%>%summarise(Class = Class, Compound = Compound,Canx=(Canx-1), 
                                                                      Dnajc5=(Dnajc5-1),
                                                                      Egfr=(Egfr-1),
                                                                      Errfi1=(Errfi1-1),
                                                                      Gapdh=(Gapdh-1),
                                                                      Kpnb1=(Kpnb1-1),
                                                                      Myc=(Myc-1),
                                                                      Nras=(Nras-1),
                                                                      P53=(P53-1),
                                                                      Rab7a=(Rab7a-1),
                                                                      RhoA=(RhoA-1),
                                                                      Rpap3=(Rpap3-1),
                                                                      Sec16a=(Sec16a-1),
                                                                      Slc2a1=(Slc2a1-1)

)







# Generating the  version and using C bind to get freq vs Int and Het vs Int


freq_long_MCF7 <- NoMod_MCF7_freq%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_freq")

int_long_MCF7 <- NoMod_MCF7_int%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_int")


het_long_MCF7 <- NoMod_MCF7_het%>%pivot_longer(cols = c(3:16),
               names_to = "gene",
               values_to ="change_het")

Cell_line<-replicate(1960,rep("MCF7"))

freq_long_MCF7<-cbind(freq_long_MCF7, Cell_line)
int_long_MCF7<-cbind(int_long_MCF7, Cell_line)
het_long_MCF7<-cbind(het_long_MCF7, Cell_line)

### freq and int NoMod ####

freq_int_long_MCF7<- cbind(freq_long_MCF7,int_long_MCF7)
freq_int_long_MCF7<-freq_int_long_MCF7[c(1:4,9,10)]
write.csv(freq_int_long_MCF7, "Output/freq_int_long_MCF7.csv", row.names = FALSE)
freq_int_long_MCF7_class<-freq_int_long_MCF7[freq_int_long_MCF7$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]


### Het and Int NoMod ####

het_int_long_MCF7<- cbind(het_long_MCF7,int_long_MCF7)
het_int_long_MCF7<-het_int_long_MCF7[c(1:4,9,10)]
write.csv(het_int_long_MCF7, "Output/het_int_long_MCF7.csv", row.names = FALSE)
het_int_long_MCF7_class<-het_int_long_MCF7[het_int_long_MCF7$Class %in% c('Bromodomain','HDAC', 'Bromodomain', 'DNMT', 'HAT', 'Methylase', 'SIRT', 'Demythylase'), ]










```



