This Script will read the spot segmentation data from the screen for HCT116 cells and generate the relative change in transcription site frequency 

```{r}
library(readr)
library (dplyr)
library(ggplot2)
library(plyr)
library(tidyverse)
library(knitr)
library(SpatialTools)
library(reshape2)
library(data.table)
library(tidyr)
library(RColorBrewer)
library(gplots)
```

Reading data

- Reading spot segmentation data for all genes


```{r}
pat<- "*cell size*"
pat_RhoA<- "*cell and size*"

paths_Slc2a1 <- dir (path = "Data/Slc2a1/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Slc2a1) <- basename(paths_Slc2a1)
total.data_Slc2a1 <-ldply (paths_Slc2a1, fread , sep = "\t")
intensity.data_Slc2a1 <- total.data_Slc2a1[c("WellName", "Nuclei Selected full cell size - Number of Spots")]
setnames(intensity.data_Slc2a1,"Nuclei Selected full cell size - Number of Spots" , "Spot" )

paths_Canx <- dir (path = "Data/Canx/", pattern = pat, full.names = TRUE, recursive = TRUE) 
names(paths_Canx) <- basename(paths_Canx)
total.data_Canx <-ldply (paths_Canx, fread , sep = "\t")
intensity.data_Canx <- total.data_Canx[c("WellName", "Nuclei Selected full cell size - Number of Spots")]
setnames(intensity.data_Canx,"Nuclei Selected full cell size - Number of Spots" , "Spot" )



 paths_RhoA <- dir (path = "Data/RhoA/", pattern = pat_RhoA, full.names = TRUE, recursive = TRUE) 
 names(paths_RhoA) <- basename(paths_RhoA)
 total.data_RhoA <-ldply (paths_RhoA, fread , sep = "\t")
 intensity.data_RhoA <- total.data_RhoA[c("WellName", "Nuclei Selected full cell and size - Number of Spots")]
 setnames(intensity.data_RhoA,"Nuclei Selected full cell and size - Number of Spots" , "Spot" )

 paths_Rpap3 <- dir (path = "Data/Rpap3/", pattern = pat, full.names = TRUE, recursive = TRUE) 
 names(paths_Rpap3) <- basename(paths_Rpap3)
 total.data_Rpap3 <-ldply (paths_Rpap3, fread , sep = "\t")
 intensity.data_Rpap3 <- total.data_Rpap3[c("WellName", "Nuclei Selected full cell size - Number of Spots")]
 setnames(intensity.data_Rpap3,"Nuclei Selected full cell size - Number of Spots" , "Spot" )



paths_Myc <- dir (path = "Data/Myc/", pattern = pat_RhoA, full.names = TRUE, recursive = TRUE) 
names(paths_Myc) <- basename(paths_Myc)
total.data_Myc <-ldply (paths_Myc, fread , sep = "\t")
intensity.data_Myc <- total.data_Myc[c("WellName", "Nuclei Selected full cell and size - Number of Spots")]
setnames(intensity.data_Myc,"Nuclei Selected full cell and size - Number of Spots" , "Spot" )


paths_Sec16a <- dir (path = "Data/Sec16a/", pattern = pat_RhoA, full.names = TRUE, recursive = TRUE) 
names(paths_Sec16a) <- basename(paths_Sec16a)
total.data_Sec16a <-ldply (paths_Sec16a, fread , sep = "\t")
intensity.data_Sec16a <- total.data_Sec16a[c("WellName", "Nuclei Selected full cell and size - Number of Spots")]
setnames(intensity.data_Sec16a,"Nuclei Selected full cell and size - Number of Spots" , "Spot" )


# old HCT data had a different file name
pat2<- "*Nuclei*"

paths_Errfi1 <- dir (path = "Data/Errfi1/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_Errfi1) <- basename(paths_Errfi1)
total.data_Errfi1 <-ldply (paths_Errfi1, fread , sep = "\t")
intensity.data_Errfi1 <- total.data_Errfi1[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Errfi1,"Nuclei Selected - Number of Spots" , "Spot" )

paths_Rab7a <- dir (path = "Data/Rab7a/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_Rab7a) <- basename(paths_Rab7a)
total.data_Rab7a <-ldply (paths_Rab7a, fread , sep = "\t")
intensity.data_Rab7a <- total.data_Rab7a[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Rab7a,"Nuclei Selected - Number of Spots" , "Spot" )




paths_Dnajc5 <- dir (path = "Data/Dnajc5/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_Dnajc5) <- basename(paths_Dnajc5)
total.data_Dnajc5 <-ldply (paths_Dnajc5, fread , sep = "\t")
intensity.data_Dnajc5 <- total.data_Dnajc5[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Dnajc5,"Nuclei Selected - Number of Spots" , "Spot" )


paths_GAPDH <- dir (path = "Data/GAPDH/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_GAPDH) <- basename(paths_GAPDH)
total.data_GAPDH <-ldply (paths_GAPDH, fread , sep = "\t")
intensity.data_Gapdh <- total.data_GAPDH[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Gapdh,"Nuclei Selected - Number of Spots" , "Spot" )


paths_Kpnb1 <- dir (path = "Data/Kpnb1/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_Kpnb1) <- basename(paths_Kpnb1)
total.data_Kpnb1 <-ldply (paths_Kpnb1, fread , sep = "\t")
intensity.data_Kpnb1 <- total.data_Kpnb1[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Kpnb1,"Nuclei Selected - Number of Spots" , "Spot" )

paths_egfr <- dir (path = "Data/egfr/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_egfr) <- basename(paths_egfr)
total.data_egfr <-ldply (paths_egfr, fread , sep = "\t")
intensity.data_Egfr <- total.data_egfr[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Egfr,"Nuclei Selected - Number of Spots" , "Spot" )

paths_nras <- dir (path = "Data/nras/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_nras) <- basename(paths_nras)
total.data_nras <-ldply (paths_nras, fread , sep = "\t")
intensity.data_Nras <- total.data_nras[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_Nras,"Nuclei Selected - Number of Spots" , "Spot" )


paths_P53 <- dir (path = "Data/P53/", pattern = pat2, full.names = TRUE, recursive = TRUE) 
names(paths_P53) <- basename(paths_P53)
total.data_P53 <-ldply (paths_P53, fread , sep = "\t")
intensity.data_P53 <- total.data_P53[c("WellName", "Nuclei Selected - Number of Spots")]
setnames(intensity.data_P53,"Nuclei Selected - Number of Spots" , "Spot" )






 
```


- Calculating  mean of the spot number

```{r}
Freq_Errfi1 <- intensity.data_Errfi1 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Errfi1 = mean (Spot)) 


Freq_Canx <- intensity.data_Canx %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Canx = mean (Spot)) 



  
Freq_Egfr <- intensity.data_Egfr %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Egfr = mean (Spot)) 

Freq_Gapdh <- intensity.data_Gapdh %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Gapdh = mean (Spot)) 


Freq_Kpnb1 <- intensity.data_Kpnb1 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Kpnb1 = mean (Spot)) 


Freq_Myc <- intensity.data_Myc %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_Myc = mean (Spot)) 


Freq_P53 <- intensity.data_P53 %>% 
  as_tibble%>% 
  group_by(WellName)%>%dplyr:::summarize ( Mean_P53 = mean (Spot)) 


Freq_RhoA <- intensity.data_RhoA %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_RhoA = mean (Spot)) 



Freq_Sec16a <- intensity.data_Sec16a %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Sec16a = mean (Spot)) 


Freq_Slc2a1 <- intensity.data_Slc2a1 %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Slc2a1 = mean (Spot)) 





 Freq_Nras <- intensity.data_Nras %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Nras = mean (Spot)) 
 
 Freq_Dnajc5 <- intensity.data_Dnajc5 %>% 
  as_tibble%>% 
 group_by(WellName)%>%dplyr:::summarize ( Mean_Dnajc5 = mean (Spot)) 

 Freq_Rab7a <- intensity.data_Rab7a %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rab7a = mean (Spot)) 

 Freq_Rpap3 <- intensity.data_Rpap3 %>% 
  as_tibble%>% 
group_by(WellName)%>%dplyr:::summarize ( Mean_Rpap3 = mean (Spot)) 
 
 
Freq_Slc2a1 <- intensity.data_Slc2a1 %>% 
  as_tibble%>% 
 group_by(WellName)%>%dplyr:::summarize ( Mean_Slc2a1 = mean (Spot)) 



 
 Freq_Combined_by_wellname <- Freq_Canx%>%
  full_join(Freq_Egfr, by = "WellName")%>%
  full_join(Freq_Errfi1, by = "WellName")%>%
  full_join(Freq_Gapdh, by = "WellName")%>%
  full_join(Freq_Kpnb1, by = "WellName")%>%
  full_join(Freq_Myc, by = "WellName")%>%
  full_join(Freq_P53, by = "WellName")%>%
  full_join(Freq_Rab7a, by = "WellName")%>%
  full_join(Freq_RhoA, by = "WellName")%>%
  full_join(Freq_Sec16a, by = "WellName")%>%
  full_join(Freq_Nras, by = "WellName")%>%
   full_join(Freq_Dnajc5, by = "WellName")%>%
   full_join(Freq_Rpap3, by = "WellName")%>%
  full_join(Freq_Slc2a1, by = "WellName")
 
Freq_Combined_by_wellname<-Freq_Combined_by_wellname
colnames(Freq_Combined_by_wellname)
```



Renaming the wells 

```{r}
Two_column_Mean_combined<- Freq_Combined_by_wellname%>%select(WellName, contains("Mean")) %>% dplyr:::rename (Canx= Mean_Canx,
                                                                      Errfi1=Mean_Errfi1,
                                                                      Egfr=Mean_Egfr,
                                                                      Gapdh=Mean_Gapdh,
                                                                      Kpnb1=Mean_Kpnb1,
                                                                      Myc=Mean_Myc,
                                                                      P53=Mean_P53,
                                                                      Rab7a=Mean_Rab7a,
                                                                      RhoA=Mean_RhoA,
                                                                      Sec16a=Mean_Sec16a,
                                                                      Nras = Mean_Nras,
                                                                      Dnajc5=Mean_Dnajc5,
                                                                      Slc2a1=Mean_Slc2a1,
                                                                      Rpap3=Mean_Rpap3)


colnames(Two_column_Mean_combined)
Full_Mean<- Two_column_Mean_combined

write.csv(Full_Mean, "Output/Collated_Freq_HCT116_raw_unfiltered.csv", row.names = FALSE)

```


- Getting Stats



```{r}


Full_Mean_b<- read.csv(file = "Output/Collated_Freq_HCT116_raw_unfiltered.csv")
sum(is.na(Full_Mean_b))


Full_Mean_pivot_b<-pivot_longer(Full_Mean_b, c(2:15), names_to = "Genes", values_to = "Mean")%>%na.omit
ggplot(Full_Mean_pivot_b, aes(y=Mean, color=Genes)) + geom_boxplot()


HCT116_Freq_Stat_before<- Full_Mean_pivot_b%>%group_by(Genes)%>%dplyr:::summarize(    
                                                         median = median(Mean), 
                                                         high = quantile(Mean, 0.75)+ 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),max= max(Mean),
                                                         nintynine= quantile(Mean, 0.95),
                                                         five= quantile(Mean, 0.05),
                                                          min = min(Mean), 
                                                         low = quantile(Mean, 0.25)- 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),
                                                          Mean= mean(Mean) )






```




Filtering the outliars based of stats and Segregating replicates and untreated samples 

```{r}
Full_Mean<- Full_Mean_b%>%
  mutate(Dnajc5 = ifelse(Dnajc5>.365, NA,Dnajc5 ))%>%
  mutate(P53 = ifelse(P53>.135, NA,Dnajc5 ))
  colnames(Full_Mean)
  sum(is.na(Full_Mean))
  
  Full_Mean_pivot<-pivot_longer(Full_Mean, c(2:15), names_to = "Genes", values_to = "Mean")%>%na.omit
ggplot(Full_Mean_pivot, aes(y=Mean, color=Genes)) + geom_boxplot()


HCT116_Freq_Stat_after<- Full_Mean_pivot%>%group_by(Genes)%>%dplyr:::summarize(    
                                                         median = median(Mean), 
                                                         high = quantile(Mean, 0.75)+ 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),max= max(Mean),
                                                         nintynine= quantile(Mean, 0.95),
                                                         five= quantile(Mean, 0.05),
                                                          min = min(Mean), 
                                                         low = quantile(Mean, 0.25)- 5*(quantile(Mean, 0.75)- quantile(Mean, 0.25 )),
                                                          Mean= mean(Mean) )

HCT116_Freq_Stat_bf <- cbind(HCT116_Freq_Stat_before, HCT116_Freq_Stat_after)
write.csv(HCT116_Freq_Stat_bf, "Output/HCT116_Freq_Stat_beforeAndAfter.csv")


Full_Mean<-Full_Mean%>%select(c("WellName" ,"Canx", "Dnajc5" , "Egfr" , "Errfi1",  "Gapdh" , "Kpnb1", "Myc" ,  "Nras" ,"P53"  ,    "Rab7a" , "Rpap3"  , "RhoA"   ,  "Sec16a"   ,      "Slc2a1"   ))
```

             Generating the files for export
- Full join the Full_mean with rep1 , rep2 and untreated wells names "replicates_average_M"
- Putting the replicates side by side and calculating the mean of the treated
- Calculating the mean median mode of the untreated and exporting the file


```{r}
#### Reading the Replicates and Untreated well names 

Replicate1<- read.csv(file = 'Metadata/Replicate1.csv')
Replicate2<- read.csv(file = 'Metadata/Replicate2.csv')
Untreated<- read.csv(file = 'Metadata/Untreated.csv')

##### Exporting the replicate and untreated data

Replicate1_Data<-Replicate1%>%left_join(Full_Mean, by = "WellName")
Replicate2_Data<-Replicate2%>%left_join(Full_Mean, by = "WellName")
Untreated_Data<-Untreated%>%left_join(Full_Mean, by = "WellName")



write.csv(Untreated_Data, "Output/HCT116_Freq_Untreated.csv", row.names=FALSE)



### printing the heterogeneity side by side

Side_By_side_HCT116<-cbind(Replicate1_Data[c(1,2)], Replicate2_Data[c(2,1)], 
            Replicate1_Data[c(1,3)], Replicate2_Data[c(3,1)],
            Replicate1_Data[c(1,4)], Replicate2_Data[c(4,1)],
            Replicate1_Data[c(1,5)], Replicate2_Data[c(5,1)],
            Replicate1_Data[c(1,6)], Replicate2_Data[c(6,1)],
            Replicate1_Data[c(1,7)], Replicate2_Data[c(7,1)],
            Replicate1_Data[c(1,8)], Replicate2_Data[c(8,1)],
            Replicate1_Data[c(1,9)], Replicate2_Data[c(9,1)],
            Replicate1_Data[c(1,10)], Replicate2_Data[c(10,1)],
            Replicate1_Data[c(1,11)], Replicate2_Data[c(11,1)],
            Replicate1_Data[c(1,12)], Replicate2_Data[c(12,1)],
            Replicate1_Data[c(1,13)], Replicate2_Data[c(13,1)],
            Replicate1_Data[c(1,14)], Replicate2_Data[c(14,1)],
            Replicate1_Data[c(1,15)], Replicate2_Data[c(15,1)]
            )
colnames(Side_By_side_HCT116)
# getting the values of the Het
replicates_M<-Side_By_side_HCT116[c(1,4,2,3,6,7,10,11,14,15,18,19,22,23,26,27,30,31,34,35,38,39, 42,43,46,47,50,51,54,55)]
colnames(replicates_M)

#Taking the mean of replicates


replicates_average_M<-replicates_M%>%
  mutate(Canx_F = rowMeans((.[,3:4]) ,na.rm=TRUE))%>%
  mutate(Dnajc5_F = rowMeans((.[,5:6]) ,na.rm=TRUE))%>%
  mutate(Egfr_F = rowMeans((.[,7:8]) ,na.rm=TRUE))%>%
  mutate(Errfi1_F = rowMeans((.[,9:10]) ,na.rm=TRUE))%>%
  mutate(Gapdh_F = rowMeans((.[,11:12]) ,na.rm=TRUE))%>%
  mutate(Kpnb1_F = rowMeans((.[,13:14]) ,na.rm=TRUE))%>%
  mutate(Myc_F = rowMeans((.[,15:16]) ,na.rm=TRUE))%>%
   mutate(Nras_F = rowMeans((.[,17:18]) ,na.rm=TRUE))%>%
  mutate(P53_F = rowMeans((.[,19:20]) ,na.rm=TRUE))%>%
  mutate(Rab7a_F = rowMeans((.[,21:22]) ,na.rm=TRUE))%>%
  mutate(Rpap3_F = rowMeans((.[,23:24]) ,na.rm=TRUE))%>%
  mutate(RhoA_F = rowMeans((.[,25:26]) ,na.rm=TRUE))%>%
  mutate(Sec16a_F = rowMeans((.[,27:28]) ,na.rm=TRUE))%>%
  mutate(Slc2a1_F = rowMeans((.[,29:30]) ,na.rm=TRUE))
  
#subsetting the _F entries only
replicates_average_M<-replicates_average_M%>%select(c(1,2) , contains("_F", ignore.case = TRUE, vars = NULL) )  # change it to include Well name

colnames(replicates_average_M)


Mean_Untreated_Freq<-colMeans(Untreated_Data[sapply(Untreated_Data, is.numeric)], na.rm = TRUE)
test<- Untreated_Data[sapply(Untreated_Data, is.numeric)]
Median_Untreated_Freq<-apply(test,2,median,na.rm = TRUE)
SD_Untreated_freq<-apply(test,2,sd,na.rm = TRUE)

Median_Untreated_Freq
Mean_Untreated_Freq
SD_Untreated_freq

Untreated_Mean_Median_SD<- cbind(Mean_Untreated_Freq,Median_Untreated_Freq, SD_Untreated_freq )
write.csv(Untreated_Mean_Median_SD, "Output/HCT116_Freq_Untreated_Mean_Median_SD.csv")





```


                      Generating the files for export

- Normalizing the values with "Mean" of untreated for both replicates and average from the dataframe "Untreated_Mean_Median_SD"
- exporting the final file with compound name and treated average


```{r}



replicates_average_mean_normalized<-replicates_average_M%>%
  mutate(Canx_F= Canx_F/.219 )%>%
  mutate(Dnajc5_F= Dnajc5_F/.124 )%>%
  mutate(Egfr_F= Egfr_F/.94 )%>%
  mutate(Errfi1_F= Errfi1_F/.823 )%>%
  mutate(Gapdh_F= Gapdh_F/.907 )%>%
  mutate(Kpnb1_F= Kpnb1_F/1.02 )%>%
  mutate(Myc_F= Myc_F/1.08 )%>%
  mutate(Nras_F= Nras_F/.437 )%>%
  mutate(P53_F= P53_F/.118 )%>%
  mutate(Rab7a_F= Rab7a_F/.861 )%>%
  mutate(Rpap3_F= Rpap3_F/.104 )%>%
  mutate(RhoA_F= RhoA_F/1.103 )%>%
  mutate(Sec16a_F= Sec16a_F/.103 )%>%
mutate(Slc2a1_F= Slc2a1_F/.263)


Replicate1_Data_mean_normalized<-Replicate1_Data%>%
  mutate(Canx= Canx/.219 )%>%
  mutate(Dnajc5= Dnajc5/.124 )%>%
  mutate(Egfr= Egfr/.94 )%>%
  mutate(Errfi1= Errfi1/.823 )%>%
  mutate(Gapdh= Gapdh/.907 )%>%
  mutate(Kpnb1= Kpnb1/1.02 )%>%
  mutate(Myc= Myc/1.08 )%>%
  mutate(Nras= Nras/.437 )%>%
  mutate(P53= P53/.118 )%>%
  mutate(Rab7a= Rab7a/.861 )%>%
  mutate(Rpap3= Rpap3/.104 )%>%
  mutate(RhoA= RhoA/1.103 )%>%
  mutate(Sec16a= Sec16a/.103 )%>%
mutate(Slc2a1= Slc2a1/.263)


Replicate2_Data_mean_normalized<-Replicate2_Data%>%
  mutate(Canx= Canx/.219 )%>%
  mutate(Dnajc5= Dnajc5/.124 )%>%
  mutate(Egfr= Egfr/.94 )%>%
  mutate(Errfi1= Errfi1/.823 )%>%
  mutate(Gapdh= Gapdh/.907 )%>%
  mutate(Kpnb1= Kpnb1/1.02 )%>%
  mutate(Myc= Myc/1.08 )%>%
  mutate(Nras= Nras/.437 )%>%
  mutate(P53= P53/.118 )%>%
  mutate(Rab7a= Rab7a/.861 )%>%
  mutate(Rpap3= Rpap3/.104 )%>%
  mutate(RhoA= RhoA/1.103 )%>%
  mutate(Sec16a= Sec16a/.103 )%>%
mutate(Slc2a1= Slc2a1/.263)


  


# renaming the columns

  colname<-colnames(replicates_average_mean_normalized)
  colname[1:2]<-c("WellName_R1", "WellName_R2")
  colnames(replicates_average_mean_normalized)<-colname
  

  

# using the existing list from xls attaching the compund name to the Mean data next to the well data 

WellNameCompound<- read.csv(file = 'Metadata/WellNameCompound.csv')
colnames(WellNameCompound)
colnames(replicates_average_mean_normalized)
replicates_average_mean_normalized_compounds<- replicates_average_mean_normalized%>%full_join(WellNameCompound, by = "WellName_R1")







# Exporting the file for heat map and analysis


write.csv(replicates_average_mean_normalized_compounds, "Output/HCT116_Freq.csv", row.names = FALSE)



write.csv(Replicate1_Data_mean_normalized, "Output/HCT116_Freq_Replicate1.csv", row.names=FALSE)
write.csv(Replicate2_Data_mean_normalized, "Output/HCT116_Freq_Replicate2.csv", row.names=FALSE)




```

Input: HCT116_Freq.csv file from line 
Output: CSV file with line 22 and 98 removed and compounds class added to the data 

Generating frequency with Class columns

```{r}
data1 <- read.csv("Output/HCT116_Freq.csv", comment.char="#")

#adding classes and ordering the data frame

class_compound<- read.csv("Metadata/Epi_Data_HBEC_Class.csv")
class_compound<-class_compound[c(1,2)] 
data1 <-data1%>% filter(!row_number() %in% c(22,98))    # removing the blank column separately 
class_compound <-class_compound%>% filter(!row_number() %in% c(22,98)) # removing the blank column separately 
data1<-cbind( class_compound,data1 ) # was not able to remoce row 22 and 98 after combining
 # removing the second reduntant compound column 19

data1<- data1[-c(19)]
colnames(data1)
sorted_class<-data1[with(data1, order(Class, Compound)),]
colnames(sorted_class)
write.csv(sorted_class, "Output/HCT116_Freq_Class_Sorted_22_98-removed.csv", row.names = FALSE)
sum(is.na(sorted_class))

```


 Using this module for the final figure. 

Input: HBEC_Freq.csv file from line 706 that has NA changed to "20"
Output: Heat map with 
        a. Sorted compound
        b. ascending gene order
        c NA left white

```{r}

colnames(sorted_class)

rnames <- sorted_class[,2]                            # assign labels in column 1 to "rnames"
mat_data <- data.matrix(sorted_class[,5:18])  # transform column 3-5 into a matrix
rownames(mat_data) <- rnames  
#print(head(mat_data))


my_palette <- colorRampPalette(c("red", "cornsilk", "blue"))(n = 299)


col_breaks = c(seq(.001,0.5,length=100),  # for red
               seq(0.51,1.5,length=100),  # for yellow
               seq(1.51,3,length=100))   #blue
              

heatmap.2(mat_data, 
           lhei = c(3,12),
           main = "HCT116_freq",
           margin=c(10,12),
          cexRow = .2,
           col= my_palette,
           breaks = col_breaks,
           trace = "none",
           dendrogram="none",
          density.info="none",
          
          Colv=FALSE, Rowv=FALSE)# for non clustered heat map



